Figures from: Vertebrate host availability and the thermal properties of mosquito-borne parasite transmission

### 2023-06-16 manuscript-figures.Rmd
clean up contact plot

## Set up density ranges
host_density_range <- c(1E-1, 1E2)
host_fixed_value <- 10
host_density_vec <- sort(c(seq(host_density_range[1], host_density_range[2],
                               length.out = resolution
), host_fixed_value))

vector_density_range <- c(0, 1E3)
vector_fixed_value <- 1000
vector_density_vec <- sort(c(seq(vector_density_range[1], vector_density_range[2],
                                 length.out = resolution
), vector_fixed_value))

@@

## Put plots together:
new_df <- contact_df %>%
  filter(`Mosquito population density` == vector_fixed_value |
           `Host population density` == host_fixed_value) %>%
  filter(`Bites per host per day` < 1E3) %>%
  select(-sigma_V, -sigma_H, -model) %>%
  melt(
    id = c(
      "Transmission model", "Bites per mosquito per day",
      "Bites per host per day"
    ),
    value.name = "x_vals"
  ) %>%
  rename(x_vars = variable) %>%
  melt(id = c("Transmission model", "x_vars", "x_vals"), value.name = "y_vals") %>%
  rename(y_vars = variable) %>%
  filter(x_vals != host_fixed_value & x_vals != vector_fixed_value) %>%
  mutate(y_max = 1.05 * y_vals) %>%
  mutate(label = case_when(
    x_vars == "Host population density" & y_vars == "Bites per mosquito per day" ~ "(a)",
    x_vars == "Mosquito population density" & y_vars == "Bites per mosquito per day" ~ "(b)",
    x_vars == "Host population density" & y_vars == "Bites per host per day" ~ "(c)",
    x_vars == "Mosquito population density" & y_vars == "Bites per host per day" ~ "(d)"
  )) %>%
  distinct()

# x = Host population density, y = Bites per mosquito per day
plot_HD_MC <- new_df %>%
  filter(x_vars == "Host population density") %>%
  filter(y_vars == "Bites per mosquito per day") %>%
  ggplot(aes(x = x_vals, y = y_vals, colour = `Transmission model`)) +
  # curves:
  geom_path(size = 1) +
  geom_blank(aes(y = y_max)) +
  # plot labels
  geom_abs_text(aes(xpos = 0.08, ypos = 0.89, label = label),
                color = "black", show.legend = FALSE
  ) +
  # x-axis:
  scale_x_log10(
    name = "",
    expand = expansion(mult = c(0, .025))
  ) +
  # y-axis:
  scale_y_continuous(
    name = "Bites per mosquito per day",
    expand = c(0, 0),
    limits = c(0, NA)
  )

# x = Mosquito population density, y = Bites per mosquito per day
plot_MD_MC <- new_df %>%
  filter(x_vars == "Mosquito population density") %>%
  filter(y_vars == "Bites per mosquito per day") %>%
  ggplot(aes(x = x_vals, y = y_vals, colour = `Transmission model`)) +
  # curves:
  geom_path(size = 1) +
  geom_blank(aes(y = y_max)) +
  # plot labels
  geom_abs_text(aes(xpos = 0.08, ypos = 0.89, label = label),
                color = "black", show.legend = FALSE
  ) +
  # x-axis:
  scale_x_log10(
    name = "",
    expand = expansion(mult = c(0, .025))
  ) +
  # y-axis:
  scale_y_continuous(
    name = "",
    expand = c(0, 0),
    limits = c(0, NA)
  ) +
  # hide legend
  guides(color = FALSE)

# x = Mosquito population density, y = Bites per host per day
plot_MD_HC <- new_df %>%
  filter(x_vars == "Mosquito population density") %>%
  filter(y_vars == "Bites per host per day") %>%
  # x = density variables, y = contact rates
  ggplot(aes(x = x_vals, y = y_vals, colour = `Transmission model`)) +
  # curves:
  geom_path(size = 1) +
  geom_blank(aes(y = y_max)) +
  # plot labels
  geom_abs_text(aes(xpos = 0.08, ypos = 0.89, label = label),
                color = "black", show.legend = FALSE
  ) +
  # x-axis:
  scale_x_log10(
    name = "Mosquito population density",
    expand = expansion(mult = c(0, .025))
  ) +
  # y-axis:
  scale_y_continuous(
    name = "",
    expand = c(0, 0),
    limits = c(0, NA)
  )

# x = Host population density, y = Bites per host per day
plot_HD_HC <- new_df %>%
  filter(x_vars == "Host population density") %>%
  filter(y_vars == "Bites per host per day") %>%
  # x = density variables, y = contact rates
  ggplot(aes(x = x_vals, y = y_vals, colour = `Transmission model`)) +
  # curves:
  geom_path(size = 1) +
  geom_blank(aes(y = y_max)) +
  # plot labels
  geom_abs_text(aes(xpos = 0.08, ypos = 0.89, label = label),
                color = "black", show.legend = FALSE
  ) +
  # x-axis:
  scale_x_log10(
    name = "Host population density",
    expand = expansion(mult = c(0, .025))
  ) +
  # y-axis:
  scale_y_continuous(
    name = "Bites per host per day",
    expand = c(0, 0),
    limits = c(0, NA)
  ) +
  # hide legend
  guides(color = FALSE)

>>>>

## Set up density ranges
host_density_range <- c(1E0, 1E3)
host_fixed_value <- 10
host_density_vec <- sort(c(10^seq(log10(host_density_range[1]), 
                                  log10(host_density_range[2]),
                                  length.out = resolution
), host_fixed_value))

vector_density_range <- c(1E0, 1E3)
vector_fixed_value <- 1000
vector_density_vec <- sort(c(10^seq(log10(vector_density_range[1]), 
                                    log10(vector_density_range[2]),
                                    length.out = resolution
), vector_fixed_value))

@@

## Put plots together:
new_df <- contact_df %>%
  filter(`Mosquito population density` == vector_fixed_value |
           `Host population density` == host_fixed_value) %>%
  # filter(`Bites per host per day` < 1E3) %>%
  select(-sigma_V, -sigma_H, -model) %>%
  melt(
    id = c(
      "Transmission model", "Bites per mosquito per day",
      "Bites per host per day"
    ),
    value.name = "x_vals"
  ) %>%
  rename(x_vars = variable) %>%
  melt(id = c("Transmission model", "x_vars", "x_vals"), value.name = "y_vals") %>%
  rename(y_vars = variable) %>%
  filter(x_vals != host_fixed_value & x_vals != vector_fixed_value) %>%
  mutate(y_max = 1.05 * y_vals) %>%
  mutate(label = case_when(
    x_vars == "Host population density" & y_vars == "Bites per mosquito per day" ~ "(a)",
    x_vars == "Mosquito population density" & y_vars == "Bites per mosquito per day" ~ "(b)",
    x_vars == "Host population density" & y_vars == "Bites per host per day" ~ "(c)",
    x_vars == "Mosquito population density" & y_vars == "Bites per host per day" ~ "(d)"
  )) %>%
  distinct()

# x = Host population density, y = Bites per mosquito per day
plot_HD_MC <- new_df %>%
  filter(x_vars == "Host population density") %>%
  filter(y_vars == "Bites per mosquito per day") %>%
  ggplot(aes(x = x_vals, y = y_vals, colour = `Transmission model`)) +
  # curves:
  geom_path(size = 1) +
  geom_blank(aes(y = y_max)) +
  # plot labels
  geom_abs_text(aes(xpos = 0.08, ypos = 0.89, label = label),
                color = "black", show.legend = FALSE
  ) +
  # x-axis:
  scale_x_log10(
    name = "",
    expand = expansion(mult = c(0, .025))
  ) +
  # y-axis:
  scale_y_continuous(
    name = "Bites per mosquito per day",
    expand = c(0, 0),
    # limits = c(0, NA)
  )

# x = Mosquito population density, y = Bites per mosquito per day
plot_MD_MC <- new_df %>%
  filter(x_vars == "Mosquito population density") %>%
  filter(y_vars == "Bites per mosquito per day") %>%
  ggplot(aes(x = x_vals, y = y_vals, colour = `Transmission model`)) +
  # curves:
  geom_path(size = 1) +
  geom_blank(aes(y = y_max)) +
  # plot labels
  geom_abs_text(aes(xpos = 0.08, ypos = 0.89, label = label),
                color = "black", show.legend = FALSE
  ) +
  # x-axis:
  scale_x_log10(
    name = "",
    expand = expansion(mult = c(0, .025))
  ) +
  # y-axis:
  scale_y_continuous(
    name = "",
    expand = c(0, 0),
    # limits = c(0, NA)
  ) +
  # hide legend
  guides(color = FALSE)

# x = Mosquito population density, y = Bites per host per day
plot_MD_HC <- new_df %>%
  filter(x_vars == "Mosquito population density") %>%
  filter(y_vars == "Bites per host per day") %>%
  # x = density variables, y = contact rates
  ggplot(aes(x = x_vals, y = y_vals, colour = `Transmission model`)) +
  # curves:
  geom_path(size = 1) +
  geom_blank(aes(y = y_max)) +
  # plot labels
  geom_abs_text(aes(xpos = 0.08, ypos = 0.89, label = label),
                color = "black", show.legend = FALSE
  ) +
  # x-axis:
  scale_x_log10(
    name = "Mosquito population density",
    expand = expansion(mult = c(0, .025))
  ) +
  # y-axis:
  scale_y_continuous(
    name = "",
    expand = c(0, 0),
    # limits = c(0, NA)
  )

# x = Host population density, y = Bites per host per day
plot_HD_HC <- new_df %>%
  filter(x_vars == "Host population density") %>%
  filter(y_vars == "Bites per host per day") %>%
  # x = density variables, y = contact rates
  ggplot(aes(x = x_vals, y = y_vals, colour = `Transmission model`)) +
  # curves:
  geom_path(size = 1) +
  geom_blank(aes(y = y_max)) +
  # plot labels
  geom_abs_text(aes(xpos = 0.08, ypos = 0.89, label = label),
                color = "black", show.legend = FALSE
  ) +
  # x-axis:
  scale_x_log10(
    name = "Host population density",
    expand = expansion(mult = c(0, .025))
  ) +
  # y-axis:
  scale_y_continuous(
    name = "Bites per host per day",
    expand = c(0, 0),
    # limits = c(0, NA)
  ) +
  # hide legend
  guides(color = FALSE)
